---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# quanteda.classifiers: Text classification textmodel extensions for quanteda

[![CRAN Version](https://www.r-pkg.org/badges/version/quanteda.classifiers)](https://CRAN.R-project.org/package=quanteda.classifiers)
[![Travis build status](https://travis-ci.org/quanteda/quanteda.classifiers.svg?branch=master)](https://travis-ci.org/quanteda/quanteda.classifiers)
[![Build status](https://ci.appveyor.com/api/projects/status/l80oet8swj2q6h4y/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/quanteda-svm/branch/master)
[![Coverage status](https://codecov.io/gh/quanteda/quanteda.classifiers/branch/master/graph/badge.svg)](https://codecov.io/github/quanteda/quanteda.classifiers?branch=master)


## Installation

```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("quanteda/quanteda.classifiers") 

keras::install_keras(method = "conda")
```

## Available classifiers

Classifier | Command
--|--
Support Vector Machine (SVM) | `textmodel_svm()`
Alternative (faster) SVM | `textmodel_svmlin()`
Sequential neural network | `textmodel_nnseq()`
Convolutional neural network + LSTM model fitted to word embeddings | `textmodel_cnnlstmemb()`

## Available human-annotated corpora

Corpus | Name
--|--
Sentence-level corpus of UK party manifestos 1945–2017, partially annotated | `data_corpus_manifestosentsUK`
Crowd-labelled sentence corpus from a 2010 EP debate on coal subsidies (in six languages) | `data_corpus_EPcoaldebate`
Large Movie Review Dataset of 50,000 annotated highly polar movie reviews for training and testing, from Maas et. al. (2011) | `data_corpus_LMRD`

## Demonstration

See this (very preliminary!) [performance comparison](https://htmlpreview.github.io/?https://github.com/quanteda/quanteda.classifiers/blob/master/tests/misc/test-LMRD.nb.html).


## How to cite

Benoit, Kenneth, Patrick Chester, and Stefan Müller (2019). quanteda.classifiers: Models for supervised text classification. R package version 0.1. URL: http://github.com/quanteda/quanteda.svm.

For a BibTeX entry, use the output from citation(package = "quanteda.classifiers").

## Issues

*  Please file an issue (with a bug, wish list, etc.) [via GitHub](https://github.com/quanteda/quanteda.classifiers/issues).

