---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# quanteda.classifiers: Text classification textmodel extensions for quanteda

[![CRAN Version](https://www.r-pkg.org/badges/version/quanteda.classifiers)](https://CRAN.R-project.org/package=quanteda.classifiers)
[![Travis build status](https://travis-ci.org/quanteda/quanteda.classifiers.svg?branch=master)](https://travis-ci.org/quanteda/quanteda.classifiers)
[![Build status](https://ci.appveyor.com/api/projects/status/l80oet8swj2q6h4y/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/quanteda-svm/branch/master)
[![Coverage status](https://codecov.io/gh/quanteda/quanteda.classifiers/branch/master/graph/badge.svg)](https://codecov.io/github/quanteda/quanteda.classifiers?branch=master)


## Installation

```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("quanteda/quanteda.classifiers") 

keras::install_keras(method = "conda")
```

## Available classifiers

Classifier | Command
--|--
Support Vector Machine (SVM) | `textmodel_svm()`
Sequential neural network | `textmodel_nnseq()`
Convolutional neural network + LSTM model fitted to word embeddings | `textmodel_cnnlstmemb()`

## Available human-annotated corpora

Corpus | Name
--|--
Sentence-level corpus of UK party manifestos 1945–2017, partially annotated | `data_corpus_manifestosentsUK`
Crowd-labelled sentence corpus from a 2010 EP debate on coal subsidies (in six languages) | `data_corpus_EPcoaldebate`

```{r, warnings=FALSE,message=FALSE}
library("quanteda.classifiers")

performance <- function(mytable, verbose = TRUE) {
  truePositives <- mytable[1, 1]
  trueNegatives <- sum(diag(mytable)[-1])
  falsePositives <- sum(mytable[1, ]) - truePositives
  falseNegatives <- sum(mytable[, 1]) - truePositives
  precision <- truePositives / (truePositives + falsePositives)
  recall <- truePositives / (truePositives + falseNegatives)
  accuracy <- sum(diag(mytable)) / sum(mytable)
  tnr <- trueNegatives / (trueNegatives + falsePositives)
  balanced_accuracy <- sum(c(precision, tnr), na.rm = TRUE) / 2
  if (verbose) {
    print(mytable)
    cat(
      "\n    precision =", round(precision, 2),
      "\n       recall =", round(recall, 2),
      "\n     accuracy =", round(accuracy, 2),
      "\n    bal. acc. =", round(balanced_accuracy, 2),
      "\n"
    )
  }
  invisible(c(precision, recall))
}

# define training texts and the "true" govt/opp status
y <- ifelse(docvars(data_corpus_dailnoconf1991, "name") == "Haughey", "Govt", NA)
y <- ifelse(docvars(data_corpus_dailnoconf1991, "name") %in% c("Spring", "deRossa"), "Opp", y)
truth <- ifelse(docvars(data_corpus_dailnoconf1991, "party") %in% c("FF", "PD"), "Govt", "Opp")

# no weighting: poor
dfm(data_corpus_dailnoconf1991) %>%
  textmodel_svm(y) %>%
  predict() %>%
  table(truth) %>%
  performance()

# proportions: poor, predicts everyone to be opposition
dfm(data_corpus_dailnoconf1991) %>%
  dfm_weight(scheme = "prop") %>%
  textmodel_svm(y) %>%
  predict() %>%
  table(truth) %>%
  performance()

# scaled - results in a fully dense dfm, and poor performance
dfm(data_corpus_dailnoconf1991) %>%
  scale() %>%
  as.dfm() %>%
  textmodel_svm(y) %>%
  predict() %>%
  table(truth) %>%
  performance()

# tf-idf: better
dfm(data_corpus_dailnoconf1991) %>%
  dfm_tfidf() %>%
  textmodel_svm(y) %>%
  predict() %>%
  table(truth) %>%
  performance()

# tf-idf: best with document frequency weights
dfm(data_corpus_dailnoconf1991) %>%
  dfm_tfidf() %>%
  textmodel_svm(y, weight = "docfreq") %>%
  predict() %>%
  table(truth) %>%
  performance()
```

## How to cite

Benoit, Kenneth, Patrick Chester, and Stefan Müller (2019). quanteda.classifiers: Models for supervised text classification. R package version 0.1. URL: http://github.com/quanteda/quanteda.svm.

For a BibTeX entry, use the output from citation(package = "quanteda.classifiers").

## Issues

*  Please file an issue (with a bug, wish list, etc.) [via GitHub](https://github.com/quanteda/quanteda.classifiers/issues).

